### 2022-02-22 pre/pre.tex
more

We assume the standard notions of $\alpha$, $\beta$ and $\eta$ conversions and
write $s \equi t$ if terms $s$ and $t$ are equal modulo $\alpha\beta\eta$
converison. We let $s \, \overline{t}_n$ stand for $s \, t_1 \, \ldots \, t_n$
and $\lam{\overline{x}_n}{s}$ for $\lambda x_1. \ldots \lambda x_n. \> s$. Every
$\beta$-reduced term can be written as $\lam{\tuple{x}{m}}{a \, \tuplen{t}}$,
where $a$ is not an application; we call $a$ the \emph{head} of the term. By
convention, $a$ and $b$ denote heads. If $a$ is a free variable, we call the term
\emph{flex}; otherwise, the term is \emph{rigid}.

@@

A {\em literal} $l$ is an equation $s \eq t$ or a disequation $s \noteq t$. A clause is a
finite multiset of literals, interpreted and written disjunctively:\ $l_1 \llor
\cdots \llor l_n$. All free variables occurring in the clause are implicitly
universally quantified. Note that $\llor$ used to denote disjunction in clauses
is different than formula-building $\ior$.

@@

\subsection{Term Order and Selection}

Superposition calculus is parametrized by a {\em reduction ordering} $\succ$, an
ordering on terms that has the following properties:

>>>>

We assume the standard notions of $\alpha$, $\beta$ and $\eta$ conversions and
write $s \equi t$ if terms $s$ and $t$ are equal modulo $\alpha\beta\eta$
converison. We let $s \, \overline{t}_n$ stand for $s \, t_1 \, \ldots \, t_n$
and $\lam{\overline{x}_n}{s}$ for $\lambda x_1. \ldots \lambda x_n. \> s$. Every
$\beta$-reduced term can be written as $\lam{\tuple{x}{m}}{a \, \tuplen{t}}$,
where $a$ is not an application; we call $a$ the \emph{head} of the term. By
convention, $a, b$ or $\zeta$ denote heads. If $a$ is a free variable, we call the term
\emph{flex}; otherwise, the term is \emph{rigid}.

@@

\looseness=-1
An {\em equation} $s \eq t$ corresponds to an unordered pair of terms. A {\em literal} $l$ is an equation $s \eq t$ or its negation (disequation) $s \noteq t$. A clause is a
finite multiset of literals, interpreted and written disjunctively:\ $l_1 \llor
\cdots \llor l_n$. Free variables of the clauses are implicitly
universally quantified. Note that $\llor$ denoting disjunction in clauses
is different than formula-building $\ior$.

@@

\subsection{Term Order and Selection}
Superposition calculus is parametrized by a {\em reduction ordering} $\succ$, an
ordering on terms that has the following properties:
